% !TeX root = ../main.tex

This paper is about detecting the surface of a badminton court on an image, using neural networks.
The paper explains \textit{Mask R-CNN} model and its historical development.
The idea for the thesis resultet from collaboration with a company named \blue{}, which operates in the badminton industry.
The main problems tackled by this paper are constructing a dataset for training the neural network, detecting the surface of the court and maximizing the accuracy.

Method of detecting the surface of the court presented in this paper is based on modified implementation of \textit{Mask R-CNN} and an artificial data generator. The paper includes the description of the method and conducted tests, as well as intructions allowing the reader to reproduce the experiments. The experiments were conducted in order to compare the results of the method with original implementation of \textit{Mask R-CNN} and a modified version. Additionally, the results of training the neural network with and without the artificial data were compared. The final results, 98\% correctly detected pixels on average, are sufficient to be used by the \blue{} company for the purpose of developing an automated judge system.

Experiments related to merging the modified \textit{Mask R-CNN} implementation with current algorithmic approach of court surface detecion used by the \blue{} company indicate a significant better performance of the automated judge system.
\\

\noindent \textbf{Keywords:} neural networks, convolutional neural networks, object detection, instance~segmentation
